Some figures to illustrate basic ideas in FDR

### 2016-10-20 analysis/IPvsEM.Rmd
Working on revisions to CompareEEvsETmodel.Rmd.
Revised ash_nplme.Rmd.

```{r chunk-options, include=FALSE}
library(REBayes)
library(ashr)
library(ggplot2)
source("chunk-options.R")
```

# Set up simulation

@@

# Summarize the results in a table.
cat("Average computation time (seconds):\n")
print(as.table(by(df,df[c("method","optmethod")],
                  function (x) mean(x$elapsed.time))))
```

# Results

@@

# Summary

>>>>

```{r chunk_options, include=FALSE}
library(REBayes)
library(ashr)
library(ggplot2)
source("chunk-options.R")
```

## Set up simulation

@@

# Summarize the results in a table.
cat("Average computation time (in seconds):\n")
print(as.table(by(df,df[c("method","optmethod")],
                  function (x) mean(x$elapsed.time))))
```

## Results

@@

## Summary

### 2016-10-20 analysis/ash_npmle.Rmd
Revised ash_nplme.Rmd.

```{r chunk-options, include=FALSE}
source("chunk-options.R")
```

@@

The following example comes from the REBayes vignette by Koenker and Gu.
The underlying $g$ is a mixture of a point mass (weight 0.8) at 0 and a point mass (weight 0.2) at 2.
```{r}
  set.seed(102)
  y <- c(rep(0,800), rnorm(200, 2)) + rnorm(1000)
  z <- REBayes::GLmix(y)
```

Now we fit the NPMLE using 'ashr' and compare with the REBayes solution.
```{r}
  grid = seq(from=min(z$x),to=max(z$x),length=1000)
  k=length(grid)
  y.ash.npmle = ashr::ash(y,1,g=ashr::unimix(pi=rep(1/(k-1),(k-1)),a=grid[-k],b=grid[-1]),method="shrink")

  plot(z$x,cumsum(z$y)/sum(z$y),col=2,main="Estimated cdf",type="l")
  lines(ashr::cdf.ash(y.ash.npmle,x=z$x),type="l")
  z$logLik
  y.ash.npmle$loglik
```

>>>>

First, we load the necessary libraries, and specify settings for
displaying the plots in the rendered document.

```{r chunk_options, include=FALSE}
library(REBayes)
library(ashr)
source("chunk-options.R")
```

@@

The following example comes from the REBayes vignette by Koenker and Gu. The
underlying $g$ is a mixture of a point mass (weight 0.8) at 0 and a point
mass (weight 0.2) at 2.
```{r fit_glmix_model}
set.seed(102)
y <- c(rep(0,800),rnorm(200,2)) + rnorm(1000)
z <- GLmix(y)
```

Now we fit the NPMLE using 'ashr' and compare with the REBayes solution.
```{r fit_ash_model}
grid = seq(from = min(z$x),to = max(z$x),length = 1000)
k    = length(grid)
y.ash.npmle =
  ash(y,1,g = unimix(pi=rep(1/(k-1),(k-1)),a = grid[-k],b = grid[-1]),
      method = "shrink")

# Plot the model fitted using GLmix against the fitted ash model.
plot(z$x,cumsum(z$y)/sum(z$y),col = 2,main = "Estimated cdf",type = "l")
lines(cdf.ash(y.ash.npmle,x = z$x),type = "l",lty = "dashed",lwd = 2)

# Compare the likelihood given the GLmix model and given ash model.
print(z$logLik,digits = 12)
print(y.ash.npmle$loglik,digits = 12)
```

### 2016-10-20 analysis/makefig_FDReg.Rmd
Revised ash_nplme.Rmd.

```{r chunk-options, include=FALSE}
require(ashr)
require(qvalue)
require(locfdr)
require(mixfdr)
source("chunk-options.R")
source("../R/plot_FDReg_hist.R")
source("../R/nullalthist.R")
```

>>>>

```{r chunk-options, include=FALSE}
require(ashr)
require(qvalue)
require(locfdr)
require(mixfdr)
source("chunk-options.R")
source("../R/plot_FDReg_hist.R")t/
source("../R/nullalthist.R")
```
